A modern, event-based architecture for distributed evolutionary algorithms

### 2018-04-03 paper.tex
Down to 12.5

  % Moved here to make it go to the top of page 3
  \begin{figure*}[t!bp]
  \includegraphics[width=0.95\textwidth]{img/kafka.png}
  \caption{Chart showing the general picture of the layers of a
    serverless architecture, including the messages and services that
    constitute KafkEO, with labels indicating message
    routes and the software components used for every part.}
  \label{fig:kafkeo}
  \end{figure*}
  %
  \section{Event based architectures and implementing evolutionary
    algorithms over them}
  \label{sec:methods}
  %
  \begin{figure*}[h!tbp]
  \includegraphics[width=0.95\textwidth]{img/kafkEO.png}
  \caption{A flow diagram of KafkEO, showing message routes, MessageHub
    topics and the functions that are being used.}
  \label{fig:kafkeo2}
  \end{figure*}
  %
  The creation of virtualization and isolation mechanisms at many
  different levels and the consequent granularization of architectures
  has led to systems that are asynchronous and loosely coupled in what
  is generally called a microservice architecture. These microservice
  architectures share the common trait of consisting of several services
  with a single concern, that is, providing a single processing value,
  in many cases stateless, and coupled using lightweight protocols such
  as REST and messaging buses that carry information from every service
  to the next. In this case, we are going to be using IBM's BlueMix
  service, which includes OpenWhisk as a serverless framework and
  MessageHub, also a vendor implementation of the Kafka messaging
  service; this last one gives name to our framework, called KafkEO (EO
  stands for Evolving Objects) and introduced in this paper.

  The main reason why we have made this choice is availability of
  resources, but also
  the fact that all parts of the implementation are open source and can
  be deployed in desktop machines or other cloud providers by changing
  the configuration, as long as it is implemented using the same tools. It is also a good practice to implement free
  software using free software, making it widely available to the
  scientific community to create their own versions or to adapt it to
  their own problems.

>>>>

  % Moved here to make it go to the top of page 3
  \begin{figure*}[t!bp]
  \includegraphics[width=0.95\textwidth]{img/kafka.png}
  \caption{Chart showing the general picture of the layers of a
    serverless architecture, including the messages and services that
    constitute KafkEO, with labels indicating message
    routes and the software components used for every part.}
  \label{fig:kafkeo}
  \end{figure*}
  %
  \section{Event-based architectures and implementing evolutionary
    algorithms over them}
  \label{sec:methods}
  %
  \begin{figure*}[h!tbp]
  \includegraphics[width=0.95\textwidth]{img/kafkEO.png}
  \caption{A flow diagram of KafkEO, showing message routes, MessageHub
    topics and the functions that are being used.}
  \label{fig:kafkeo2}
  \end{figure*}
  % Talked about this earlier: - M
  %The creation of virtualization and isolation mechanisms at many
  %different levels and the consequent granularization of architectures
  %has led to systems that are asynchronous and loosely coupled in what
  %is generally called a microservice architecture.

  %These microservice
  Microservice architectures share the common trait of consisting of several services with a single concern, that is, providing a single processing value,
  in many cases stateless, and coupled using lightweight protocols such
  as REST and messaging buses that carry information from every service
  to the next. In this case, we are going to be using IBM's BlueMix
  service, which includes OpenWhisk as a serverless framework and
  MessageHub, a vendor implementation of the Kafka messaging
  service; this last one gives name to the framework we are presenting, called KafkEO (EO stands for Evolving Objects).

  The main reason for choosing OpenWhisk and Kafka is availability of
  resources, but also the fact that all parts of the implementation are open source and can be deployed in desktop machines or other cloud providers by changing the configuration. It is also a good practice to implement free
  software using free software, making it widely available to the
  scientific community.
  % to create their own versions or to adapt it to their own problems.
